---
title: "Remote Work"
subtitle: "Section 1: Intro and Data"
author: "Michael Foley"
date: "8/1/2021"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: flatly
    highlight: haddock
    fig_width: 9
    fig_caption: false
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r warning=FALSE, message=FALSE, include=FALSE}
library(tidyverse)
library(flextable())
library(mice)
library(patchwork)
```

Buffer published its report [The 2021 State of Remote Work](https://buffer.com/2021-state-of-remote-work) based on a survey collected in late 2020. The report was a follow up to its [2020 report](https://lp.buffer.com/state-of-remote-work-2020), featured in [MakeoverMonday](https://data.world/makeovermonday/2020w32) (with wonderful takes on the data). The [2021 report data]("https://docs.google.com/spreadsheets/d/1aJFW-_Rq3xNa2Fos-raoA1sF23CwT9sLAfHopjMZnLs/edit?usp=sharing") is also available as a Google sheets file on Google Docs.

The survey found that workers overwhelmingly support remote work. However, they do reveal struggles. I am curious what factors impact their struggles. 

In this section, I pull the 2021 report data from Google Docs and prepare it for analysis in the  subsequent sections. 

```{r include=FALSE, class.source='fold-hide'}
buffer_url <- "https://docs.google.com/spreadsheets/d/1aJFW-_Rq3xNa2Fos-raoA1sF23CwT9sLAfHopjMZnLs/edit?usp=sharing"

codebook <- tribble(
  ~item, ~desc, ~resp_type,
  "country", "What country do you live in currently?", "c",
  "industry", "What industry do you work in?", "c",
  "industry_other", "Other", "c",
  "role", "In the following list, what best describes the work you do?", "c",
  "role_other", "Other", "c",
  "race", "Which of the following best describes you?", "c",
  "race_other", "Other", "c",
  "work_exp", "How long have you been in the workforce?", "c",
  "remote_exp", "How long have you worked remotely?", "c",
  "disability", "Do you have a disability or chronic illness?", "d",
  "disability_remote", "Is a disability or chronic illness one of the reasons you pursued remote work?", "d",
  "caregiver", "Are you a parent or caregiver?", "d",
  "caregiver_remote", "Is being a parent or caregiver one of the reasons you pursued remote work?", "d",
  "prefer_remote", "Would you like to work remotely, at least some of the time, for the rest of your career?", "d",
  "recommend_remote", "Would you recommend remote work to others?", "d",
  "struggle", "What’s your biggest struggle with working remotely?", "c",
  "struggle_other", "Other", "c",
  "benefit", "What’s the biggest benefit you see to working remotely?", "c",
  "benefit_other", "Other", "c",
  "covid", "Are you working remotely as a result of COVID-19?", "d",
  "permanent", "Is your company planning on permanently allowing remote work?", "c",
  "return", "When will you be returning to your workspace and no longer be allowed to work remotely?", "c",
  "smooth", "Was your company's transition to remote work smooth?", "d",
  "smooth_why", "What made it smooth?", "c",
  "smooth_not", "Why not?", "c",
  "change", "What has changed the most about your work now that you work remotely?", "c",
  "change_other", "Other", "c",
  "work_less_more", "Would you say you are working less or more now that you work remotely?", "c",
  "meet_more", "Do you find you are in more meetings as a result of the shift to remote work?", "d",
  "other_changes", "Is there anything else you'd like to add about how your work has changed now that you work remotely?", "c",
  "emp_type", "Which description best suits you?", "c",
  "time_zones", "Is your company operating in multiple time zones?", "d",
  "time_zones_cnt", "How many time zones do employees at your company span?", "c",
  "time_zones_team", "Are people on your immediate team in multiple time zones?", "d",
  "asynch", "Does your company encourage asynchronous communication?", "d",
  "fte", "How many full-time employees does your company have?", "c",
  "pct_remote", "What percentage of your company works remotely?", "c",
  "pay_internet", "If you work from home, does your company pay for your home internet?", "c",
  "pay_cell", "Does your company pay for your cell phone?", "c",
  "pay_membership", "Does your company cover the cost of a coworking membership?", "c",
  "pay_computer", "Does your company cover your necessary hardware needs?", "c",
  "pay_software", "Does your company cover your necessary software needs?", "c",
  "pay_other", "Are there any other costs of working remotely that your company covers?", "c",
  "other", "Anything else you want to add that we didn’t ask about?", "c"
)
```

## File Download

The file is located on Google Docs.

```{r collapse=TRUE}
googlesheets4::gs4_deauth() # not using a private sheet, so no need for token
buffer_0 <- googlesheets4::read_sheet(
  buffer_url,
  range = "CompleteData!B3:AS2248",
  col_names = codebook$item,
  col_types = paste(codebook$resp_type, collapse = ""))

dim(buffer_0)
```

Here is my handmade codebook. There are 44 vars.

```{r}
codebook %>% 
  select(-resp_type) %>%
  flextable() %>%
  autofit() %>%
  theme_zebra() %>%
  set_caption("Codebook.")
```

## Delete Empty Rows

Several records are completely empty. They are easily spotted as having no value in the first column (country).

```{r}
buffer_1 <- buffer_0 %>%
  filter(!is.na(country))

dim(buffer_1)
```

That trims our data set from `r {nrow(buffer_0)} %>% scales::comma()` to `r {nrow(buffer_1)} %>% scales::comma()` rows. 

## Remove "Other" Cols

Several multiple-choice questions have a free-form "other" option. There won't be much predictive power in the "other" values, so I will replace the null vales with the string "Other", and remove the "other" columns.

```{r}
buffer_2 <- buffer_1 %>%
  replace_na(list(industry = "Other",
                  role = "Other",
                  race = "Other/Unk",
                  struggle = "Other",
                  benefit = "Other",
                  change = "Other"
                  )) %>%
  select(-contains("other"), pay_other) 

dim(buffer_2)
```

That trims our data set from `r {ncol(buffer_1)} %>% scales::comma()` to `r {ncol(buffer_2)} %>% scales::comma()` cols.

## Remove Uninteresting Cols

A few questions about the company paying for particular attributes of remote work are not interesting. Same is true with time-zone distribution of company employees. 

```{r}
codebook %>% 
  filter(str_detect(item, "^pay|(time_zones)|(^asynch)")) %>%
  select(-resp_type)
```

I'll drop them all.

```{r}
buffer_3 <- buffer_2 %>%
  select(-starts_with(c("pay", "time", "asynch")))

dim(buffer_3)
```

That trims our data set from `r {ncol(buffer_2)} %>% scales::comma()` to `r {ncol(buffer_3)} %>% scales::comma()` cols.

## Remove Free-Form Cols

Free-form survey items are not useful here either.

```{r}
codebook %>%
  filter(item %in% c("smooth_why", "smooth_not", "change")) %>%
  select(-resp_type)
```

```{r}
buffer_4 <- buffer_3 %>%
  select(-c(smooth_why, smooth_not, change))

dim(buffer_4)
```

That trims our data set from `r {ncol(buffer_3)} %>% scales::comma()` to `r {ncol(buffer_4)} %>% scales::comma()` cols.

## Remove Sparse Cols

A few columns are more than 50% empty.

```{r}
(na_vars <- buffer_4 %>%
  skimr::skim() %>%
  filter(complete_rate < .5))
```

Imputing values is possible, but I'm less concerned with prediction than I am with understanding variable importance. I'll remove them.

```{r}
buffer_5 <- buffer_4 %>%
  select(-na_vars$skim_variable)
```

```{r}
skimr::skim(buffer_4)
```


## Characters to Factors

Most of the character fields need to be factors if they are going to be useful in models.

```{r}
buffer_6 <- buffer_5 %>%
  mutate(race = factor(case_when(race == "Asian or Pacific Islander" ~ "Asian",
                                 race == "Black or African American" ~ "Black",
                                 race == "Hispanic or Latino" ~ "Hispanic",
                                 race == "Multiracial or Biracial" ~ "Multiracial",
                                 race == "Native American or Alaska Native" ~ "Other/Unk",
                                 TRUE ~ race),
                       levels = c("White", "Black", "Hispanic", "Asian", "Multiracial", "Other/Unk")),
         work_exp = factor(work_exp, levels = c("Less than six months",
                                                "6 months - 11 months",
                                                "1 year - 4 years",
                                                "5 years - 9 years",
                                                "10 years - 14 years", 
                                                "15 years - 19 years",
                                                "More than 20 years"),
                           ordered = TRUE),
         remote_exp = factor(remote_exp, levels = c("Less than six months",
                                                "6 months to 11 months",
                                                "1 year to 4 years",
                                                "5 years - 9 years",
                                                "More than 10 years")),
         disability = factor(disability, levels = c(0, 1), labels = c("No", "Yes")),
         emp_type = factor(emp_type, levels = c("Business owner", 
                                                "Employee",
                                                "Freelancer / Self-employed"),
                           labels = c("Business Owner", "Employee", "Self-Employed")),
         role = case_when(role == "Customer Support" ~ "CSR",
                          role == "Human Resources" ~ "HR",
                          role == "Marketing and Advertising" ~ "Marketing",
                          TRUE ~ role),
         role = fct_relevel(role, "Other", after = Inf),
         covid = factor(covid, levels = c(0, 1), labels = c("Not Related", "COVID-Related")),
         prefer_remote = factor(prefer_remote, levels = c(0, 1), labels = c("No Remote", "Prefer")),
         recommend_remote = factor(recommend_remote, levels = c(0, 1), labels = c("No Remote", "Recommend")),
         caregiver = factor(caregiver, 
                            levels = c(0, 1), 
                            labels = c("Not Caregiver", "Caregiver")),
         benefit = factor(benefit, 
                          levels = c("Ability to have a flexible schedule",
                                     "Ability to spend time with family",
                                     "Ability to work from home",
                                     "Flexibility to work from any location",
                                     "Not having to commute",
                                     "Other"),
                          labels = c("Flexible Schedule", "Time with Family",
                                     "Work from Home", "Flexible Location",
                                     "No Commute", "Other")),
         industry = factor(industry),
         fte = factor(fte, levels = c("Just me",
                                      "Fewer than 10", 
                                      "11 to 50",
                                      "51 to 100",
                                      "101 to 500", 
                                      "501 to 1,000",
                                      "More than 1,001")),
         pct_remote = factor(pct_remote, levels = c("1 to 25%",
                                                    "26 to 50%",
                                                    "51 to 75%", 
                                                    "76 to 99%",
                                                    "100%")),
         struggle = factor(struggle, 
                           levels = c("Being in a different timezone than teammates",
                                      "Difficulties with collaboration and communication",
                                      "Distractions at home",
                                      "Loneliness",
                                      "Not being able to unplug",
                                      "Staying motivated",
                                      "Other"),
                           labels = c("Timezones", "Collaboration", 
                                      "Distractions", "Loneliness", "Unplugging",
                                      "Motivation", "Other"))) %>%
         select(-contains("other"), -contains("time_zones"), -starts_with("pay"))
```

## Impute Null Values

Some values are null, but might be inferred as another value. I'll use the mode for `disability`, and the median for `caregiver`.

```{r}
buffer_7 <- buffer_6 %>%
  replace_na(list(disability = "No",
                  caregiver = "Not Caregiver"))
```

I'll use **mice** to impute `fte` and `pct_remote`.  

```{r}
set.seed(2020)
mice_obj <- mice(buffer_7)
buffer_8 <- complete(mice_obj)
```

```{r}
p1 <- data.frame(original = buffer_7$fte, mice = buffer_8$fte) %>%
  pivot_longer(cols = c("original", "mice"), names_to = "Data", values_to= "Fare") %>%
  ggplot(aes(x = Fare, fill = Data)) + 
  geom_bar(na.rm = TRUE, position = position_dodge()) +
  ggthemes::scale_fill_few() +
  theme_light() + 
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 90)) +
  labs(subtitle = "fte", x = NULL, y = NULL, fill = "")

p2 <- data.frame(original = buffer_7$pct_remote, mice = buffer_8$pct_remote) %>%
  pivot_longer(cols = c("original", "mice"), names_to = "Data", values_to= "Fare") %>%
  ggplot(aes(x = Fare, fill = Data)) + 
  geom_bar(na.rm = TRUE, position = position_dodge()) +
  ggthemes::scale_fill_few() +
  theme_light() + 
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90)) +
  labs(subtitle = "pct_remote", x = NULL, y = NULL, fill = "")

p1 + p2 +
  patchwork::plot_annotation(title = "Mice Imputations")
```

## Final Look

```{r}
skimr::skim(buffer_8)
```


## Save Data

```{r}
saveRDS(buffer_8, file = "./buffer.rds")
saveRDS(codebook, file = "./codebook.rds")
```

